\section{Related Literature}

The decline in real interest rates in recent decades is noted by \citet{summers2014reflections}, claiming that the lack of investment opportunities along with raised private saving propensities and reduced investment propensities. His approach determines a macroeconomic framework around the Global Financial Crisis and the Eurozone crisis. On the other hand, \citet{rogoff2022} argues that the decline in the long-term real interest rates is not particular to recent decades. Instead, it is a trend stationary and persistent decline that dates back to the 1300s. This long-term decline, according to \citet{rogoff2022}, reflects the reduced discount factors over time at the global scale and challenges explanations around productivity and demographics. \\

Shifting the perspective on the decline of real interest rates to financial markets and monetary policy, in their study, \citet{gilchrist2014us} presented that the longer-term interest rates in advanced economies, proxied by 10-year bond yields, were declined in response to both an unanticipated conventional easing and unconventional monetary actions of the Fed. While conventional monetary easing steepens the yield curve in advanced economies through a larger decline in the short-end of the yield curve, unconventional monetary actions narrow the yield spread of nominal foreign interest rates down. Moreover, \citet{hanson2015monetary} documented that the changes in monetary policy affect the 10-year forward real rates, utilizing movements during the FOMC announcement days. They offer a ``reaching for yield'' mechanism such that the yield-oriented investors substitute for longer-term bonds as short-term yields decline if the yield curve is upward-sloping. In turn, increasing demand for longer maturity bonds leads to increasing prices and declining yields. That is, this explanation relies on a ``term premium'' effect. \citep{hanson2015monetary}\\

% Add a few studies similar to Gilchrist and Hanson


On the other hand, starting from \citet{romer2004new} and \citet{gurkaynak2005}, there is a growing literature on identifying high-frequency monetary policy shocks. \citet{nakamura2018high} provide a comprehensive analysis of the ``Fed information effect'' and monetary non-neutrality by examining high-frequency interest rate changes around FOMC meetings, i.e., monetary policy announcements influence not only financial variables but also adjust the beliefs and expectations of private sector participants about economic trajectory. By incorporating the adjustment of private sector expectations, the authors reveal that a considerable portion of the observed responses in real interest rates can be attributed to changes in perceptions of the natural rate of interest, emphasizing the dual role of monetary policy in shaping expectations. Yet, later on, \citet{bauer2023alternative} propesed the “Fed Response to news” hypothesis, challenging the “Fed information effect”. Using both high-frequency data around the FOMC meetings and publicly available economic news into their identification strategy, their findings suggest that rather than the Fed retaining superior and market-moving information, along with the market participants, the Fed also react similarly to public economic information. \\

% hillenbrand'ı kopyala yapıştır yaptım
In a recent study, \citet{hillenbrand2022} states that previous studies posit structural macroeconomic factors to explain the interest rate decline such as ``global savings glut'' or ``demand shortfall'', whereas a narrow time window around the FOMC announcements captures the secular decline in U.S. Treasury yields from the 1980s. Out-of-window yield changes appears to be transitory and ``wash out over time'' \citep{hillenbrand2022}. Consequently, underlining mechanisms like dot-plots, the author proposes ``Long-run Fed Guidance'', stating that the Fed has a superior information set on the long-run path of interest rates, thus guiding the market expectation of investors. 

\newpage 

Heretofore, I discussed the literature on the monetary policy and declining real interest rates, depicted in bond yields. Nevertheless, another line of research that is indispensable for this study, is on the ``Global Financial Cycle'', which is elaborated in \citet{miranda2015world}, \citet{miranda2020us} and \citet{rey2021}. \citet{miranda2020us} demonstrated that a single global factor explains around one-fifth of a common variation of the risky asset prices around the world. Given that the U.S. dollar is the dominant currency of global banking, one instance of this is that almost \%80 of the syndicated loans that have an average amount greater than \$5 million are denominated in the U.S. dollar, the monetary policy decisions by the Fed have a direct impact over the Global Financial Cycle. The potential explanations for this phenomenon are the deleveraging of the financial intermediaries around the globe, and relatedly, a decline in global credit and gross capital flows, and a significant rise in aggregate risk aversion. \citep{miranda2020us} In their work on surrender options in life insurance and market interest rates, \citet{kubitza2023life} estimates two-stage least-squares regressing German government bond rates on the U.S. monetary policy shocks, claiming a transmission through the international bond market channel.
