\section{Data and Institutional Background}

This section involves providing background information on the institutional background of the central banks' mechanisms for monetary decision-making for each country in the sample. Later, I elaborate on both yield data and monetary policy decision data, including the number of observations and time intervals.

\subsection{Eurozone}

In the European Central Bank (ECB), the Governing Council is the principal decision-making entity for conducting monetary policy. The Governing Council consists of twenty-six members---six members of the Executive Board and the Euro-area national central bank governors.\footnote{European Central Bank, \textit{Governing Council}, available at \href{https://www.ecb.europa.eu/ecb/decisions/govc/html/index.en.html}{ecb.europa.eu/govc}} While the Governing Council members meet twice a month to evaluate macroeconomic and financial conditions, it decides monetary policy stance every six weeks. The Governing Council conducts monetary policy through three key interest rates: the main refinancing operations rate, the deposit facility rate, and the marginal lending facility rate. I obtained the dates of monetary policy decisions from the ECB website. My sample contains in total 299 monetary policy decision dates, from March 1999 to March 2024. To remove potential heterogeneity due to credit risk between different European countries, I selected Germany, and collected on-the-run yield data on 10-year German Bunds.

\subsection{United Kingdom}

In the United Kingdom, the Monetary Policy Committee (MPC) is the key decision-making body of the Bank of England (BoE) to conduct monetary policy. The MPC is made up of nine members, including the Governor, the Deputy Governors for Monetary Policy, Financial Stability, and Markets and Banking, the Chief Economist, and four external members.\footnote{Bank of England, \textit{Monetary Policy Committee}, available at \href{https://www.bankofengland.co.uk/about/people/monetary-policy-committee}{bankofengland.co.uk/mpc}} The main interest rate set by the MPC to drive monetary policy is the `Bank Rate', which refers to the interest rate BoE pays to commercial banks that hold money with the BoE. The dates of monetary policy decisions are collected from the BoE's voting history database, ranging from June 1997 to March 2024, and the total number of data points is 295. I collected yield data of the UK government bonds, also known as gilts, from 1979 to 2024 from the BoE database. The yield data contains the estimation for zero-coupon continuously-compounded yields, computations are elaborated in \citet{anderson2001new}.

\subsection{Japan}
In Japan, the key decision-making body for conducting monetary policy is the Policy Board of the Bank of Japan (BoJ). Similar to the MPC of the BoE, the Policy Board of BoJ also consists of nine members---the Governor, two Deputy Governors, and six other members. The Bank of Japan uses the Policy-Rate Balance to conduct monetary policy as its main tool, which refers to the interest rate for the policy-rate balances that financial institutions hold at the central bank.\footnote{Bank of Japan, \textit{Outline of Monetary Policy}, available at \href{https://www.boj.or.jp/en/mopo/outline/index.htm}{boj.or.jp/mopo}} In the dataset on monetary policy decision dates by the BoJ, there are 515 data points, ranging from December 1981 to March 2024. The interest rates on government bonds are collected from the database of Japanese Ministry of Finance, and computed using on-the-run securities.


\subsection{Canada}

In Canada, the Governing Council of the Bank of Canada is the decision-making body for conducting monetary policy and promoting a more resilient financial system. The Governing Council comprises six members: the Governor, the Senior Deputy Governor, and four Deputy Governors. The Council uses the policy interest rate as a main tool for conducting monetary policy, and the rate is typically set on eight predetermined announcement dates annually, with decisions reached by consensus rather than through individual votes. Within the sample, there are 175 monetary policy decision dates spanning from January 1999 to April 2024, and for the yield data, I consulted the Bank of Canada's own data sources, from which \citet{bolder2004empirical} constructed the historical zero-coupon yield curve data.


\subsection{Switzerland}
The Governing Board, the Swiss National Bank's (SNB) executive body for monetary policy decisions, comprises three members appointed for six-year terms by the Federal Council upon the recommendation of the Bank Council.\footnote{Swiss National Bank, \textit{Supervisory and Management Boards}, available at \href{https://www.snb.ch/en/the-snb/organisation/supervisory-management-boards}{snb.ch/supervisory-boards}} The Governing Board holds the primary responsibility for formulating monetary policy. The SNB conducts -monetary policy through setting the policy rate, aiming the alignment of short-term Swiss franc money market rates with the policy rate, indicating a different policy mandate than previous central banks in sample. The data on the monetary policy decision dates spans from January 2000 to March 2024, with a total number of 109 meetings. Yield data, referred to as the spot interest rates, represent the yields on zero-coupon bonds computed by the extended Nelson-Siegel procedure by the SNB.

\subsection{Australia}

The Reserve Bank of Australia (RBA) conducts monetary policy through its key executive body, the Reserve Bank Board. Again, similar to the executive bodies of the BoE and BoJ, the Reserve Bank Board comprises nine members---the Governor, the Deputy Governor, the Secretary to the Treasury, and six other members.\footnote{Reserve Bank of Australia, \textit{RBA Board}, available at \href{https://www.rba.gov.au/about-rba/boards/rba-board.html}{rba.gov.au/rba-board}} The Board holds meetings eight times a year for decision-making of the monetary policy. The primary monetary policy instrument utilized by the RBA is the ``cash rate target'', which is the interest rate on overnight loans in the money market, and this rate influences a range of interest rates across the economy. For my analysis, I collected the dates of monetary policy decisions from the RBA, spanning from August 1992 to March 2024, which includes a total of 215 meetings. Additionally, I collected yield data of Australian government bonds from January 1995 to May 2024 from the Reserve Bank of Australia's database. The yields are computed and interpolated by the RBA.
